---
title: "More 10T"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: false
---
```{r load data, include = F, warning = F}
library(plotly)
library(heatmaply)
library(ggplot2)
library(gplots)
library(viridis)
```

The other page is getting long.

## PCA with top 500 most variable {.tabset .tabset-pills .tabset-fade}
Taking the top 500 most variable genes among the samples and generating a regular old Euclidean distance matrix.

### Annot+TE
```{r tripca1, echo = F, warning = F}
load("D:/PhD/Analysis/10T/reinnier.RData")
All_HM

```

### Annot only
```{r tripca2, echo = F, warning = F}
ENS_HM
```

### TE only
```{r tripca3, echo = F, warning = F}
TE_HM
```

## {.unlisted .unnumbered}

<details>
<summary>Size Factors</summary>
**Size factor all entries**
```
                   dds.sizeFactor
H33K36M_C3H10T1_1       1.9754626
H33K36M_C3H10T1_2       0.7887794
H33K36M_C3H10T1_3       0.3056923
H33K36R_C3H10T1_1       1.3801394
H33K36R_C3H10T1_2       0.3812469
H33K36R_C3H10T1_3       0.3979667
NSD12DKO_C3H10T1_1      1.9744437
NSD12DKO_C3H10T1_2      0.7853220
NSD12DKO_C3H10T1_3      0.6446567
PA_C3H10T1_1            2.1517784
PA_C3H10T1_2            0.3786161
PA_C3H10T1_3            0.8761740
SETD2KO_C3H10T1_1       2.3758762
SETD2KO_C3H10T1_2       0.6693181
SETD2KO_C3H10T1_3       0.4933132
TKO_C3H10T1_1           2.7458456
TKO_C3H10T1_2           2.6752406
TKO_C3H10T1_3           2.9033106
```

**Size factor annot only**
```
                   ddsSub.sizeFactor
H33K36M_C3H10T1_1          1.9958859
H33K36M_C3H10T1_2          0.7398523
H33K36M_C3H10T1_3          0.2721026
H33K36R_C3H10T1_1          1.3409255
H33K36R_C3H10T1_2          0.3396584
H33K36R_C3H10T1_3          0.3556429
NSD12DKO_C3H10T1_1         1.9671956
NSD12DKO_C3H10T1_2         0.7176141
NSD12DKO_C3H10T1_3         0.5812148
PA_C3H10T1_1               2.1461076
PA_C3H10T1_2               0.3208860
PA_C3H10T1_3               0.7840284
SETD2KO_C3H10T1_1          2.3940446
SETD2KO_C3H10T1_2          0.6030431
SETD2KO_C3H10T1_3          0.4408191
TKO_C3H10T1_1              4.0540994
TKO_C3H10T1_2              4.1465894
TKO_C3H10T1_3              4.1640333 
```

</details>

## Normalized using size factors of only protein coding genes
`grep 'protein_coding' annotation.gtf | perl -ne '/^.+?\tgene\t.+?"(ENSMUS.+?)".+$/ && print $1`

```{r sf, echo = F, warning = F}
load("D:/PhD/Analysis/10T/C3hsizeFactor.RData")
buttonplotSF

```